Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Create guidelines
Add hours

\itemize{
  \item{
    subsection \ref{subsec:guidelines}: guidelines for empiricists
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
  \item{
    subsection \ref{subsec:non_clock}: the effect when the alignment
    is generated by a non-clock like nucleotide substitution model
  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of mutations
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
  \item{
    subsection \ref{subsec:better_label_needed} shows 
    \richel{better description needed}
  }
}

@@

\itemize{
  \item the use of 20 replicates results in decent plots
  \item the use of more taxa, counterintuitively, increases the inference error
  \item the use of longer DNA sequences, as expected, decreases the inference error
  \item {
    there is a difference when a twin alignment is selected to have
    an equal amount of mutations as the true alignment. The consequences
    of this is unknown
  }
  \item using a mutation rate less than 1.0 / crown age, decreases the
    inference error. We predict this will increase the error in the parameter
    estimation
  } 
}

@@

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github("richelbilderbeek/pirouette")
\end{lstlisting}
To start using \verb;pirouette;, 
load its functions in the global namespace first:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
library(pirouette)
\end{lstlisting}
Because \verb;pirouette; calls BEAST2, BEAST2 must be installed. 
This can be done from within R, using:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
install_beast2()
\end{lstlisting}
For the option to select the best candidate model,
\verb;pirouette; needs the "NS" BEAST2 package [\cite{russel2019model}].
It can be installed from within R, using:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
install_beast2_pkg("NS")
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{ | l | l | l | }
    \hline
    \textbf{Name} & \textbf{Description} & \textbf{Listing} \\
    \hline
    \verb;pir_run; & Run \verb;pirouette; & \ref{lst:pir_run} \\
    \verb;pir_plot; & Show the \verb;pirouette; results as a plot & \ref{lst:pir_plot} \\
    \verb;create_pir_params; & Create the \verb;pirouette; parameters & \ref{lst:create_pir_params} \\
    \hline
    \verb;create_alignment_params; & Create the alignment parameters & \ref{lst:create_alignment_params} \\
    \verb;create_twinning_params; & Create the twinning parameters & \ref{lst:create_twinning_params} \\
    \verb;create_experiment; & Create one experiment & \ref{lst:create_gen_experiment_explicit} \\
    \verb;create_error_measure_params; & Create the error measurement parameters & \ref{lst:create_error_measure_params} \\
    \hline
  \end{tabular}
  \caption{
    \texttt{pirouette}'s main functions, description and the number of the 
    listing in which it is used. 
  }
  \label{tab:functions}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_19/errors.png}
  \caption{500 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{1000 nucleotides (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_34/errors.png}
  \caption{2000 nucleotides}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_27/errors.png}
  \caption{An unlinked node substitution model, 20 replicates}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_22/errors.png}
  \caption{Assuming a Yule tree prior on a Yule tree}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_26/errors.png}
  \caption{Assuming a Yule tree prior on a BD tree}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_23}.

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/errors.png}
  \caption{Equal mutation rate}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Equal mutation rate and number of mutations (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_35/errors.png}
  \caption{Per-nucleotide mutation rate of 0.25 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_36/errors.png}
  \caption{Per-nucleotide mutation rate of 0.50 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_37/errors.png}
  \caption{Per-nucleotide mutation rate of 0.75 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Per-nucleotide mutation rate of 1.0 / crown age (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_38/errors.png}
  \caption{Per-nucleotide mutation rate of 1.25 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_39/errors.png}
  \caption{Per-nucleotide mutation rate of 1.50 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_40/errors.png}
  \caption{Per-nucleotide mutation rate of 2.0 / crown age}
\end{figure}

>>>>

\itemize{
  \item{
    subsection \ref{subsec:guidelines}: guidelines for empiricists
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
  \item{
    subsection \ref{subsec:non_clock}: the effect when the alignment
    is generated by a non-clock like nucleotide substitution model
  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of mutations
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
}

@@

\itemize{
  \item the use of 20 replicates results in decent plots
  \item the use of more taxa, counterintuitively, increases the inference error
  \item the use of longer DNA sequences, as expected, decreases the inference error
  \item {
    there is a difference when a twin alignment is selected to have
    an equal amount of mutations as the true alignment. The consequences
    of this is unknown
  }
  \item {
    using a mutation rate less than 1.0 / crown age, decreases the
    inference error. We predict this will increase the error in the parameter
    estimation
  }
}

@@

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github(
  "richelbilderbeek/pirouette"
)
\end{lstlisting}
To start using \verb;pirouette;, 
load its functions in the global namespace first:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
library(pirouette)
\end{lstlisting}
Because \verb;pirouette; calls BEAST2, BEAST2 must be installed. 
This can be done from within R, using:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
install_beast2()
\end{lstlisting}
For the option to select the best candidate model,
\verb;pirouette; needs the "NS" BEAST2 package [\cite{russel2019model}].
It can be installed from within R, using:
\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
install_beast2_pkg("NS")
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{ | l | l | l | }
    \hline
    \textbf{Name} & \textbf{Description} \\
    \hline
    \verb;pir_run; & Run \verb;pirouette; \\
    \verb;pir_plot; & Show the \verb;pirouette; results as a plot  \\
    \verb;create_pir_params; & Create the \verb;pirouette; parameters  \\
    \hline
    \verb;create_alignment_params; & Create the alignment parameters  \\
    \verb;create_twinning_params; & Create the twinning parameters  \\
    \verb;create_experiment; & Create one experiment  \\
    \verb;create_error_measure_params; & Create the error measurement parameters  \\
    \hline
  \end{tabular}
  \caption{
    \texttt{pirouette}'s main functions and description. 
  }
  \label{tab:functions}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_19/errors.png}
  \caption{500 nucleotides, 12 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{1000 nucleotides, 17 hours (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_34/errors.png}
  \caption{2000 nucleotides, 11 hours}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_27/errors.png}
  \caption{An unlinked node substitution model, 20 replicates, 8 hours}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_22/errors.png}
  \caption{Assuming a Yule tree prior on a Yule tree, 9 hours}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_26/errors.png}
  \caption{Assuming a Yule tree prior on a BD tree, 9 hours}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_23}
and took 120 hours in total.

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/errors.png}
  \caption{Equal mutation rate, 10 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Equal mutation rate and number of mutations, 19 hours (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_35/errors.png}
  \caption{Per-nucleotide mutation rate of 0.25 / crown age, 11 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_36/errors.png}
  \caption{Per-nucleotide mutation rate of 0.50 / crown age, 14 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_37/errors.png}
  \caption{Per-nucleotide mutation rate of 0.75 / crown age, 16 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Per-nucleotide mutation rate of 1.0 / crown age, 19 hours (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_38/errors.png}
  \caption{Per-nucleotide mutation rate of 1.25 / crown age, 17 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_39/errors.png}
  \caption{Per-nucleotide mutation rate of 1.50 / crown age, 10 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_40/errors.png}
  \caption{Per-nucleotide mutation rate of 2.0 / crown age, 19 hours}
\end{figure}
